Avoiding tipping points in ecosystem based fisheries management: a non-parametric Bayesian approach

### 2014-05-13 manuscripts/manuscript.Rmd
fix typo in figure5 chunk opts

```{r Figure5, dependson=c("sim"), fig.cap="Gaussian process inference outperforms parametric estimates. Shown are 100 replicate simulations of the stock dynamics (eq 1) under the policies derived from each of the estimated models, as well as the policy based on the exact underlying model." fig.width=6, fig.height=6}
ggplot(sims_data) + 
  geom_line(aes(time, fishstock, group=interaction(reps,method), color=method), alpha=.1) +
  scale_colour_manual(values=colorkey, guide = guide_legend(override.aes = list(alpha = 1))) + 
  facet_wrap(~method) + guides(legend.position="none")

>>>>

```{r Figure_5, dependson=c("sim"), fig.cap="Gaussian process inference outperforms parametric estimates. Shown are 100 replicate simulations of the stock dynamics (eq 1) under the policies derived from each of the estimated models, as well as the policy based on the exact underlying model.", fig.width=6, fig.height=6}
ggplot(sims_data) + 
  geom_line(aes(time, fishstock, group=interaction(reps,method), color=method), alpha=.1) +
  scale_colour_manual(values=colorkey, guide = guide_legend(override.aes = list(alpha = 1))) + 
  facet_wrap(~method) + guides(legend.position="none")
